---
title: "Diarrhea_ud_five"
author: "Yawo"
date: "2025-01-09"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load package
```{r message=FALSE, warning=FALSE}
rm(list = ls())
library(dplyr)
library(INLA)
library(stats)
library(data.table)
library(tidyverse)
library(here)
library(sf)
library(sp)
library(spdep)
library(dlnm)
library(tsModel)
library(hydroGOF)
library(RColorBrewer)
library(openxlsx)
library(readxl)
library(splines)
library(geofacet)
library(ggpubr)
library(ggthemes)
```

#load data
```{r}
grid_data<- read.xlsx("grid_data.xlsx")
#sf_data
map <- read_sf("gadm41_RWA_shp/gadm41_RWA_2.shp")%>%
  left_join(grid_data, by= c("NAME_2"= "District_name")) %>% 
  rename(Province = NAME_1) %>% 
  mutate(Province = case_when(
    Province == "Amajyaruguru" ~ "North",
    Province == "Amajyepfo" ~ "South",
    Province == "Iburasirazuba" ~ "East",
    Province == "Iburengerazuba" ~ "West",
    Province == "Umujyi wa Kigali" ~ "Kigali City"
  )) %>% select(Province, District = NAME_2)

# Create adjacency matrix
nb.map <- poly2nb(as_Spatial(map$geometry))
g.file <- "output4/map.graph"
if (!file.exists(g.file)) nb2INLA(g.file, nb.map)
#health and climate data

data<-read_rds("Climate_Diarrhea_ERA5.rds")%>%
mutate(time = (Year - 2016) * 12 + Month)%>%
left_join(grid_data, by= c("District"= "District_name"))%>% 
arrange(District_code)%>% 
mutate(Province_code= code_num)%>%select(-name, -code_num)

```


#set variables

```{r}
# set maximum lag
nlag = 2

# total number of months
ntime <- length(unique(data$time))
# total number of years
nyear <- length(unique(data$Year))
# total number of Districts
ndistrict <- length(unique(data$District_code))
# total number of province
nprovince <- length(unique(data$Province_code))

```

#set cross-bais matrix

```{r}
 #define cross-basis matrix (combining nonlinear exposure and lag functions)
# set lag knots
lagknot = equalknots(0:nlag, 2)

# Temp1
var <- subset(data, select = c("temp1", paste0("lag", 1:nlag)))
basis_tmax1 <- crossbasis(var,
                    argvar = list(fun = "ns", knots = equalknots(data$temp1, 2)),
                    arglag = list(fun = "ns", knots = nlag/2))

# Temp
var <- subset(data, select = c("temp", paste0("tp_lag", 1:nlag)))
basis_tmax <- crossbasis(var,
                         argvar = list(fun = "ns", knots = equalknots(data$temp, 2)),
                         arglag = list(fun = "ns", knots = nlag/2))

# rainfall
var <- subset(data, select = c("rainfall", paste0("r_lag", 1:nlag)))
basis_rainfall <- crossbasis(var,
                         argvar = list(fun="ns", knots = equalknots(data$rainfall, 2)),
                         arglag = list(fun="ns", knots = lagknot))

# tprainfall
var <- subset(data, select = c("tprainfall", paste0("rtp_lag", 1:nlag)))
basis_tprainfall<- crossbasis(var,
                         argvar = list(fun="ns", knots = equalknots(data$tprainfall, 2)),
                         arglag = list(fun="ns", knots = lagknot))


# assign unique column names to cross-basis matrix for inla() model
# note: not necessary for glm(), gam() or glm.nb() models
colnames(basis_tmax1) = paste0("basis_tmax1.", colnames(basis_tmax1))
colnames(basis_tmax) = paste0("basis_tmax.", colnames(basis_tmax))
colnames(basis_rainfall) = paste0("basis_rainfall.", colnames(basis_rainfall))
colnames(basis_tprainfall) = paste0("basis_tprainfall.", colnames(basis_tprainfall))


```


# create indices for INLA models
```{r}
# note: for INLA models an index should start with 1 and with the max value equal to the length of unique values

# create district index 
data$district_index <- rep(1:ndistrict, ntime)

# create district index 
k <- unique(data$District_code)

for (j in 1:ndistrict)
{
  data$district_index[data$District_code == k[j]] <- j 
}


# create Province index
# state length
k <- unique(data$Province_code)

for (j in 1:nprovince)
{
  data$province_index[data$Province_code == k[j]] <- j 
}

# create year index
# set first year (in this case 2019) to 1
data$year_index <- data$Year - 2018 
```


# set up data and priors for INLA model
```{r}
# set data for models
Y  <- data$Diarrhea_Hosp_OPD_ud_five # response variable
N  <- length(Y) # total number of data points
data$E  <- data$tot_pop*sum(data$Diarrhea_Hosp_OPD_ud_five, na.rm=TRUE)/sum(data$tot_pop, na.rm=TRUE) # model offset so that response is equivalent to an incidence rate per 100,000 people
data$SIR <- data$Diarrhea_Hosp_OPD_ud_five/data$E
E <-  data$E
T1 <- data$Month # for random effect to account for annual cycle (seasonality)
T2 <- data$year_index # for random effect to account for inter-annual variability
S1 <- data$district_index # for district spatial random effect
S2 <- data$province_index # for province interaction with month random effect

# create dataframe for model testing
df <- data.frame(Y, E, T1, T2, S1, S2)

# define priors
precision.prior <- list(prec = list(prior = "pc.prec", param = c(0.5, 0.01)))

# inla model function

# include formula and set defaults for data, family (to allow other prob dist models e.g. Poisson) and config (to allow for sampling)
mymodel <- function(formula, data = df, family = "poisson", config = FALSE)

  {
  model <- inla(formula = formula, data = data, family = family, offset = log(E),
       control.inla = list(strategy = 'adaptive'), 
       control.compute = list(dic = TRUE, config = config, 
                              cpo = TRUE, return.marginals = FALSE),
       control.fixed = list(correlation.matrix = TRUE, 
                            prec.intercept = 1, prec = 1),
       control.predictor = list(link = 1, compute = TRUE), 
       verbose = FALSE)
  model <- inla.rerun(model)
  return(model)
}
```

# run models of increasing complexity in INLA

```{r}
# Step 1: Fit a baseline model including spatiotemporal random effects
# Base model includes:
# - State-specific monthly random effects (random walk cyclic prior)
# - Year-specific spatial random effects (BYM2 prior)

# Define baseline formula
baseformula <- Y ~ 1 + 
  f(T1, replicate = S2, model = "rw2", cyclic = TRUE, constr = TRUE,
    scale.model = TRUE, hyper = precision.prior) +
  f(S1, model = "bym2", replicate = T2, graph = "output4/map.graph", 
    scale.model = TRUE, hyper = precision.prior)

# test baseline model with Negative Binomial distribution
# model <- mymodel(baseformula, family = "nbinomial")
# model$dic$dic

# Define formulas by adding Tmax and rainfall cross-basis functions
formula0.1 <- update.formula(baseformula, ~ . + basis_tmax)
formula0.2 <- update.formula(baseformula, ~ . + basis_tprainfall)
formula0.3 <- update.formula(baseformula, ~ . + basis_tmax + basis_tprainfall)

# Create a list of formulas and corresponding labels
formulas <- list(baseformula, formula0.1, formula0.2, formula0.3)
lab <- c("basemodel", "model0.1", "model0.2", "model0.3")

# Fit models and save results
models <- lapply(seq_along(formulas), function(i) {
  cat("Fitting model:", lab[i], "\n")  # Progress message
  model <- mymodel(formulas[[i]], df)
  save(model, file = file.path("output4", paste0(lab[i], ".RData")))
  return(model)
})

# Create a table to store DIC values
table0 <- data.table(Model = c("base", "tmax", "rainfall", "tmax + rainfall"), DIC = NA)

# Populate DIC values from saved models
for (i in seq_along(lab)) {
  file_path <- file.path("output4", paste0(lab[i], ".RData"))
  if (file.exists(file_path)) {
    load(file_path)
    if (!is.null(model$dic$dic)) {
      table0$DIC[i] <- round(model$dic$dic, 0)
    } else {
      cat("Warning: DIC not found for", lab[i], "\n")
    }
  } else {
    cat("Warning: File not found for", lab[i], "\n")
  }
}

# View the resulting DIC table
print(table0)
# define position of best fitting model
best.fit <- which.min(table0$DIC)
```


```{r}
# assign formula for best fitting model to the new baseformula
#baseformula <- formulas[[best.fit]]

# redefine baseformula as best fitting model from above
baseformula <- Y ~ 1 + f(T1, replicate = S2, model = "rw2", cyclic = TRUE, constr = TRUE,
                         scale.model = TRUE,  hyper = precision.prior) +
  f(S1, model = "bym2", replicate = T2, graph = "output4/map.graph", 
    scale.model = TRUE, hyper = precision.prior) + basis_tmax + basis_tprainfall

# Step 1: compare models using goodness of fit statistics

# create a table to store model adequacy results (DIC, CV log score, MAE difference results)
# create model label string
mod.name <- c("basemodel", "model0.1", "model0.2", "model0.3")

table1 <- data.table(Model = mod.name, 
                     DIC = NA,
                     logscore = NA)

# create loop to read in model object and extract DIC and CV log score
for (i in 1:length(mod.name))
{
  load(paste0("Output4/", mod.name[i],".RData"))
  # add model fit statistics from each model to table
  table1$DIC[i] <- round(model$dic$dic,0)
  table1$logscore[i] <- round(-mean(log(model$cpo$cpo), na.rm = T), 3)
}

# save model adequacy results for all models (Appendix Table S1) 
fwrite(table1, file = "figs4/table_S01.csv", quote = FALSE, 
          row.names = FALSE) 
```

```{r}
# load baseline and selected model
load("output4/basemodel.RData")
basemodel <- model
load("output4/model0.3.RData")
```

# Visualise random effects for selected model


```{r}

# explore spatial and temporal random effects 

# plot monthly random effects per state (Appendix Fig S7)
month_effects <- data.frame(Province_code = rep(unique(data$Province_code), each = 12),
                            Month = model$summary.random$T1)

# plot monthly random effects per province
month_effects <- month_effects %>% 
  # add the predefined state grid by state code
  left_join(grid_data %>% select(-District_name, -District_code) %>% unique, 
            by = c("Province_code" = "code_num")) 

month_effects <- map %>% select(-District) %>% unique() %>% left_join(month_effects, by = c("Province" = "name"))

month_effects %>% 
  ggplot() + 
  geom_ribbon(aes(x = Month.ID, ymin = `Month.0.025quant`, ymax = `Month.0.975quant`), 
              fill = "cadetblue4", alpha = 0.5) + 
  geom_line(aes(x = Month.ID, y = Month.mean), col = "cadetblue4") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey70") +
  xlab("Month") +
  ylab("Contribution to log(Diarrhe_cases)") +
  scale_y_continuous() +
  scale_x_continuous(breaks = c(1,4,7,10), labels = c("Jan", "Apr", "Jul", "Oct")) +
  theme_bw() + 
  # organise by Province name in grid file
  facet_wrap(~Province)
  # facet_geo( ~name, grid = grid_data)
  
ggsave("figs4/fig_S06_month_effect.pdf", height = 30, width = 25, units = "cm")
```

#DNLM result

# Country level
```{r}
# load model output

# Load best fitting model with climate DLNMs 
load("output4/model0.3.RData")
model0 <- model

# Step 1: plot tmax output
# Select the climate best model
model <- model0

# Extract full coef and vcov and create indicators for each term
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Find position of the terms associated with tmax crossbasis
indt <- grep("basis_tmax", model$names.fixed)

# Extract predictions from the tmax DLNM centred on overall mean Tmax (26 deg C)
predt <- crosspred(basis_tmax, coef = coef[indt], vcov = vcov[indt, indt],
                   model.link = "log", bylag = 0.25, cen = round(mean(data$temp, na.rm = TRUE), 0))

# Contour and scenario plots for tmax (Main text Fig 3)
# Contour plot of exposure-lag-response associations (Main text Fig 3a)
pdf("figs4/fig_03a_tmax_contour.pdf", width = 6.5, height = 6)

# Variables for plotting
y <- predt$predvar
x <- seq(0, nlag, 0.25)
z <- t(predt$matRRfit)

# Define color palettes and levels
pal <- rev(brewer.pal(11, "PRGn"))
levels <- pretty(range(z, na.rm = TRUE), 20)
col1 <- colorRampPalette(pal[1:6])
col2 <- colorRampPalette(pal[6:11])
cols <- c(col1(sum(levels <= 1)), col2(sum(levels > 1)))

# Generate filled contour plot
filled.contour(
  x, y, z,
  xlab = "Lag",
  ylab = expression(paste("Temperature (", degree, "C)")),
  main = "Diarrhea Under Five",
  col = cols,
  levels = levels,
  plot.axes = {
    axis(1, at = 0:nlag, labels = 0:nlag)  # Customize x-axis
    axis(2)  # Customize y-axis
    mtext(side = 2, at = max(y) * 0.95, text = "a", las = 2, cex = 1.2, line = 2)
  }
)

# Close PDF device
if (dev.cur() > 1) dev.off()
```

## Relative Risk plot by Temperature Range Using allRRfit
```{r}
# Output plot as a high-resolution PNG
png("figs4/fig_relative_risk_temperature23.png", width = 800, height = 800, res = 150)

# Extract exposure values and relative risk data
vars <- predt$predvar
rr <- predt$allRRfit  # Use aggregated relative risks
rr.lci <- predt$allRRlow  # Lower bound of confidence interval
rr.uci <- predt$allRRhigh  # Upper bound of confidence interval

# Ensure exposure and RR data are finite
if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
  stop("Missing values found in input data. Check the 'predt' object.")
}

# Set y-axis limits dynamically based on RR range
r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

# Plot Relative Risk by Temperature Range
plot(vars, rr, type = "l", col = "red", lwd = 2,
     xlab = "Temperature (°C)", ylab = "Relative Risk",
     main = "Diarrhea Relative Risk by Temperature Range",
     ylim = c(r1, r2 * 1.1), frame.plot = TRUE)

# Add shaded confidence interval
polygon(c(vars, rev(vars)), 
        c(rr.lci, rev(rr.uci)), 
        col = adjustcolor("red", alpha.f = 0.3), border = NA)

# Add horizontal reference line at RR = 1
abline(h = 1, lty = 2, col = "gray")

# Add legend
legend("topright", legend = "Relative Risk by Temperature", col = "red", lwd = 2, bty = "n")

# Save and close the PNG device
dev.off()

```


### Relative Risk plot by Temperature Range Using matRRfit
```{r}
# Output plot as a high-resolution PNG
png("figs4/fig_relative_risk_temperature.png", width = 800, height = 800, res = 150)

# Get exposure values
vars <- predt$predvar

# Ensure exposure values and RR data are finite
rr <- predt$matRRfit
rr.lci <- predt$matRRlow
rr.uci <- predt$matRRhigh

# Ensure there are no NA values in the data
if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
  stop("Missing values found in input data. Check 'predt' object.")
}

# Set colors for different temperature ranges
col <- colorRampPalette(brewer.pal(11, "RdBu"))(length(vars))

# Set y-axis limits dynamically based on RR range
r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

# Plot Relative Risk by Temperature Range
plot(vars, rr[, 1], type = "l", col = col[1], lwd = 2,
     xlab = "Temperature (°C)", ylab = "Relative Risk",
     main = "Diarrhea Under Five Relative Risk by Temperature Range",
     ylim = c(r1, r2 * 1.1), frame.plot = TRUE, axes = TRUE)

polygon(c(vars, rev(vars)),
        c(rr.lci[, 1], rev(rr.uci[, 1])),
        col = adjustcolor(col[1], alpha.f = 0.3), border = NA)

# Add horizontal reference line at RR = 1
abline(h = 1, lty = 2, col = "gray")

# Add a legend for temperature ranges
legend("topright",
       legend = c("Relative Risk by Temperature Range"),
       col = col[1], lwd = 2, lty = 1, bty = "n")

# Save and close the PNG device
dev.off()

```

#temp scenario (save plot as image)

## Lag Response Plot for Different Tmax Scenarios

```{r}
# Output plot as a high-resolution PNG
png("figs4/fig_03b_tmax_scenario.png", width = 800, height = 800, res = 150)

# Get exposure values
vars <- predt$predvar

# Ensure exposure values and RR data are finite
rr <- predt$matRRfit
rr.lci <- predt$matRRlow
rr.uci <- predt$matRRhigh
lagbylag <- seq(0, ncol(rr) - 1) * 0.25

# Ensure there are no NA values in the data
if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
  stop("Missing values found in input data. Check 'predt' object.")
}

# Get indices for selected temperature scenarios
mn <- which.min(abs(vars - 20))  # Cool scenario (20°C)
mx <- which.min(abs(vars - 25))  # Warm scenario (25°C)
mx2 <- which.min(abs(vars - 30)) # Warmest scenario (30°C)

# Define colors and transparency for scenarios
col1 <- brewer.pal(11, "RdBu")[9]  # Cool scenario
tcol1 <- adjustcolor(col1, alpha.f = 0.3)

col2 <- brewer.pal(11, "RdBu")[3]  # Warm scenario
tcol2 <- adjustcolor(col2, alpha.f = 0.3)

col3 <- brewer.pal(11, "RdBu")[1]  # Warmest scenario
tcol3 <- adjustcolor(col3, alpha.f = 0.3)

# Set y-axis limits dynamically based on RR range
r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

# Plot the Cool scenario
plot(lagbylag, rr[mn, ], col = col1, type = "l", lwd = 2,
     xlab = "Lag (Month)", ylab = "Relative Risk",
     main = "Lag Response for Different Temperature Scenarios",
     ylim = c(r1, r2 * 1.1), frame.plot = TRUE, axes = FALSE)
axis(1, at = seq(0, max(lagbylag), 1), labels = seq(0, max(lagbylag), 1))
axis(2)
polygon(c(lagbylag, rev(lagbylag)),
        c(rr.lci[mn, ], rev(rr.uci[mn, ])),
        col = tcol1, border = NA)

# Plot the Warm scenario
lines(lagbylag, rr[mx, ], col = col2, lwd = 2)
polygon(c(lagbylag, rev(lagbylag)),
        c(rr.lci[mx, ], rev(rr.uci[mx, ])),
        col = tcol2, border = NA)

# Plot the Warmest scenario
lines(lagbylag, rr[mx2, ], col = col3, lwd = 2)
polygon(c(lagbylag, rev(lagbylag)),
        c(rr.lci[mx2, ], rev(rr.uci[mx2, ])),
        col = tcol3, border = NA)

# Add horizontal reference line at RR = 1
abline(h = 1, lty = 2, col = "gray")

# Add a legend
legend("topright",
       legend = c(paste0("Temp = ", round(vars[mn], 1), "°C"),
                  paste0("Temp = ", round(vars[mx], 1), "°C"),
                  paste0("Temp = ", round(vars[mx2], 1), "°C")),
       col = c(col1, col2, col3), lwd = 2, lty = 1, bty = "n")

# Add subplot label
mtext(side = 2, line = 3, text = "b", las = 2, cex = 1.2, adj = 0.9)

# Save and close the PNG device
dev.off()

```


#Province level plot

```{r}
# Load model output
load("output4/model0.3.RData")
model0 <- model

# Open a single PDF file for all provinces
pdf("figs4/fig_03a_tmax_contour_all_provinces.pdf", width = 12, height = 12)

# Set up a consistent layout for the plots (1 per page)
par(mfrow = c(2,1 ))  # One plot per page

# Iterate over unique provinces
provinces <- unique(data$Province)
for (province in provinces) {
  # Filter data for the current province
  province_data <- subset(data, Province == province)

  # Set the model for the province
  model <- model0

  # Extract full coef and vcov for the province
  coef <- model$summary.fixed$mean
  vcov <- model$misc$lincomb.derived.covariance.matrix

  # Find position of terms associated with tmax crossbasis
  indt <- grep("basis_tmax", model$names.fixed)

  # Extract predictions from the tmax DLNM centered on overall mean Tmax
  mean_temp <- round(mean(province_data$temp, na.rm = TRUE), 0)
  predt <- crosspred(basis_tmax, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_temp)

  # Variables for plotting
  y <- predt$predvar
  x <- seq(0, nlag, 0.25)
  z <- t(predt$matRRfit)

  # Define color palettes and levels
  pal <- rev(brewer.pal(11, "PRGn"))
  levels <- pretty(range(z, na.rm = TRUE), 20)
  col1 <- colorRampPalette(pal[1:6])
  col2 <- colorRampPalette(pal[6:11])
  cols <- c(col1(sum(levels <= 1)), col2(sum(levels > 1)))

  # Generate filled contour plot
  filled.contour(
    x, y, z,
    xlab = "Lag month",
    ylab = expression(paste("Temperature (", degree, "C)")),
    main = paste("Contour Plot for", province),
    col = cols,
    levels = levels,
    plot.axes = {
      axis(1, at = 0:nlag, labels = 0:nlag)  # Customize x-axis
      axis(2)  # Customize y-axis
    }
  )
}

# Close the PDF device after all plots
dev.off()

```


##Relative Risk plot by Temperature Range for Each Province allRRfit

```{r}

# Set up a PDF output device for all plots
pdf("figs4/fig_relative_risk_temperature_all_provinces23.pdf", width = 10, height = 10)

provinces <- unique(data$Province)
layout(matrix(1:length(provinces), nrow = ceiling(sqrt(length(provinces))))) # Arrange plots in a grid
par(mfrow = c(3, 2)) 
for (province in provinces) {
  # Filter data for the current province
  province_data <- subset(data, Province == province)
  
  # Extract predictions for the current province (assuming predt setup)
  mean_temp <- round(mean(province_data$temp, na.rm = TRUE), 0)
  predt <- crosspred(basis_tmax, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_temp)
  
  # Extract exposure values and relative risk data
vars <- predt$predvar
rr <- predt$allRRfit  # Use aggregated relative risks
rr.lci <- predt$allRRlow  # Lower bound of confidence interval
rr.uci <- predt$allRRhigh  # Upper bound of confidence interval

# Ensure exposure and RR data are finite
if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
  stop("Missing values found in input data. Check the 'predt' object.")
}

# Set y-axis limits dynamically based on RR range
r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

# Plot Relative Risk by Temperature Range
plot(vars, rr, type = "l", col = "red", lwd = 2,
     xlab = "Temperature (°C)", ylab = "Relative Risk",
     main = paste("Diarrhea Relative Risk by Temperature for", province),
     ylim = c(r1, r2 * 1.1), frame.plot = TRUE)

# Add shaded confidence interval
polygon(c(vars, rev(vars)), 
        c(rr.lci, rev(rr.uci)), 
        col = adjustcolor("red", alpha.f = 0.3), border = NA)

# Add horizontal reference line at RR = 1
abline(h = 1, lty = 2, col = "gray")

# Add legend
legend("topright", legend = "Relative Risk by Temperature", col = "red", lwd = 2, bty = "n")

}

# Close the PDF device
dev.off()

```

##Relative Risk plot by Temperature Range for Each Province matRRfit

```{r}

# Set up a PDF output device for all plots
pdf("figs4/fig_relative_risk_temperature_all_provinces.pdf", width = 10, height = 10)

provinces <- unique(data$Province)
layout(matrix(1:length(provinces), nrow = ceiling(sqrt(length(provinces))))) # Arrange plots in a grid
par(mfrow = c(3, 2)) 
for (province in provinces) {
  # Filter data for the current province
  province_data <- subset(data, Province == province)
  
  # Extract predictions for the current province (assuming predt setup)
  mean_temp <- round(mean(province_data$temp, na.rm = TRUE), 0)
  predt <- crosspred(basis_tmax, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_temp)
  
  # Get exposure values
  vars <- predt$predvar

  # Ensure exposure values and RR data are finite
  rr <- predt$matRRfit
  rr.lci <- predt$matRRlow
  rr.uci <- predt$matRRhigh

  # Ensure there are no NA values in the data
  if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
    stop("Missing values found in input data. Check 'predt' object.")
  }

  # Set colors for different temperature ranges
  col <- colorRampPalette(brewer.pal(11, "RdBu"))(length(vars))

  # Set y-axis limits dynamically based on RR range
  r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
  r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

  # Plot Relative Risk by Temperature Range
  plot(vars, rr[, 1], type = "l", col = col[1], lwd = 2,
       xlab = "Temperature (°C)", ylab = "Relative Risk",
       main = paste("Diarrhea Under Five Relative Risk by Temperature for", province),
       ylim = c(r1, r2 * 1.1), frame.plot = TRUE, axes = TRUE)

  polygon(c(vars, rev(vars)),
          c(rr.lci[, 1], rev(rr.uci[, 1])),
          col = adjustcolor(col[1], alpha.f = 0.3), border = NA)

  # Add horizontal reference line at RR = 1
  abline(h = 1, lty = 2, col = "gray")

  # Add a legend for temperature ranges
  legend("topright",
         legend = c("Relative Risk by Temperature Range"),
         col = col[1], lwd = 2, lty = 1, bty = "n")
}

# Close the PDF device
dev.off()

```

## contour Plot by district

```{r}
# Load model output
load("output4/model0.3.RData")
model0 <- model

# Open a single PDF file for all districts
pdf("figs4/fig_03a_tmax_contour_all_districts.pdf", width = 12, height = 12)

# Set up a 2x2 grid for four plots per page
par(mfrow = c(2, 2))  # Two rows and two columns

# Initialize plot counter
plot_count <- 0

# Iterate over unique districts
districts <- unique(data$District)
for (district in districts) {
  # Filter data for the current district
  district_data <- subset(data, District == district)

  # Set the model for the district
  model <- model0

  # Extract full coef and vcov for the district
  coef <- model$summary.fixed$mean
  vcov <- model$misc$lincomb.derived.covariance.matrix

  # Find position of terms associated with tmax crossbasis
  indt <- grep("basis_tmax", model$names.fixed)

  # Extract predictions from the tmax DLNM centered on overall mean Tmax
  mean_temp <- round(mean(district_data$temp, na.rm = TRUE), 0)
  predt <- crosspred(basis_tmax, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_temp)

  # Variables for plotting
  y <- predt$predvar
  x <- seq(0, nlag, 0.25)
  z <- t(predt$matRRfit)

  # Define color palettes and levels
  pal <- rev(brewer.pal(11, "PRGn"))
  levels <- pretty(range(z, na.rm = TRUE), 20)
  col1 <- colorRampPalette(pal[1:6])
  col2 <- colorRampPalette(pal[6:11])
  cols <- c(col1(sum(levels <= 1)), col2(sum(levels > 1)))

  # Generate filled contour plot
  filled.contour(
    x, y, z,
    xlab = "Lag",
    ylab = expression(paste("Temperature (", degree, "C)")),
    main = paste("Contour Plot for", district),
    col = cols,
    levels = levels,
    plot.axes = {
      axis(1, at = 0:nlag, labels = 0:nlag)  # Customize x-axis
      axis(2)  # Customize y-axis
    }
  )

  # Increment plot counter
  plot_count <- plot_count + 1

  # Start a new page after every four plots
  if (plot_count %% 4 == 0) {
    par(mfrow = c(2, 2))  # Reset 2x2 grid for the next page
  }
}

# Close the PDF device after all plots
dev.off()

```


###Relative Risk plot by Temperature Range for Each district allRRfit

```{r}
# Set up a PDF output device
pdf("figs4/fig_relative_risk_temperature_all_districts23.pdf", width = 10, height = 10)

# Extract unique districts
districts <- unique(data$District)

# Set up a 2x2 grid for four plots per page
par(mfrow = c(2, 2))  # Two rows and two columns per page

# Counter for plot tracking
plot_count <- 0

# Loop through each district
for (district in districts) {
  # Filter data for the current district
  district_data <- subset(data, District == district)
  
  # Calculate the mean temperature for centering (if applicable)
  mean_temp <- round(mean(district_data$temp, na.rm = TRUE), 0)
  
  # Extract predictions for the current district
  predt <- crosspred(basis_tmax, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_temp)
  
   # Extract exposure values and relative risk data
vars <- predt$predvar
rr <- predt$allRRfit  # Use aggregated relative risks
rr.lci <- predt$allRRlow  # Lower bound of confidence interval
rr.uci <- predt$allRRhigh  # Upper bound of confidence interval

# Ensure exposure and RR data are finite
if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
  stop("Missing values found in input data. Check the 'predt' object.")
}

# Set y-axis limits dynamically based on RR range
r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

# Plot Relative Risk by Temperature Range
plot(vars, rr, type = "l", col = "red", lwd = 2,
     xlab = "Temperature (°C)", ylab = "Relative Risk",
     main = paste("Diarrhea Relative Risk by Temperature for", district),
     ylim = c(r1, r2 * 1.1), frame.plot = TRUE)

# Add shaded confidence interval
polygon(c(vars, rev(vars)), 
        c(rr.lci, rev(rr.uci)), 
        col = adjustcolor("red", alpha.f = 0.3), border = NA)

# Add horizontal reference line at RR = 1
abline(h = 1, lty = 2, col = "gray")

# Add legend
legend("topright", legend = "Relative Risk by Temperature", col = "red", lwd = 2, bty = "n")
  # Increment plot counter
  plot_count <- plot_count + 1
  
  # Start a new page after every four plots
  if (plot_count %% 4 == 0) {
    par(mfrow = c(2, 2))  # Reset the 2x2 grid for the next page
  }
}

# Close the PDF device
dev.off()

```

##Relative Risk plot by Temperature Range for Each district matRRfit
```{r}
# Set up a PDF output device
pdf("figs4/fig_relative_risk_temperature_all_districts.pdf", width = 10, height = 10)

# Extract unique districts
districts <- unique(data$District)

# Set up a 2x2 grid for four plots per page
par(mfrow = c(2, 2))  # Two rows and two columns per page

# Counter for plot tracking
plot_count <- 0

# Loop through each district
for (district in districts) {
  # Filter data for the current district
  district_data <- subset(data, District == district)
  
  # Calculate the mean temperature for centering (if applicable)
  mean_temp <- round(mean(district_data$temp, na.rm = TRUE), 0)
  
  # Extract predictions for the current district
  predt <- crosspred(
    basis_tmax, 
    coef = coef[indt], 
    vcov = vcov[indt, indt],
    model.link = "log", 
    bylag = 0.25, 
    cen = mean_temp
  )
  
  # Get exposure values and relative risks
  vars <- predt$predvar
  rr <- predt$matRRfit
  rr.lci <- predt$matRRlow
  rr.uci <- predt$matRRhigh
  
  # Ensure there are no missing values
  if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
    stop("Missing values found in input data. Check 'predt' object.")
  }

  # Set colors for the plot
  col <- colorRampPalette(brewer.pal(11, "RdBu"))(length(vars))

  # Set y-axis limits dynamically based on RR range
  r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
  r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

  # Plot Relative Risk by Temperature Range for the district
  plot(vars, rr[, 1], type = "l", col = col[1], lwd = 2,
       xlab = "Temperature (°C)", ylab = "Relative Risk",
       main = paste("Diarrhea Under Five Relative Risk by Temperature for", district),
       ylim = c(r1, r2 * 1.1), frame.plot = TRUE, axes = TRUE)

  # Add confidence intervals as shaded areas
  polygon(c(vars, rev(vars)),
          c(rr.lci[, 1], rev(rr.uci[, 1])),
          col = adjustcolor(col[1], alpha.f = 0.3), border = NA)

  # Add horizontal reference line at RR = 1
  abline(h = 1, lty = 2, col = "gray")

  # Add a legend for temperature ranges
  legend("topright",
         legend = c("Diarrhea Under Five Relative Risk by Temperature Range"),
         col = col[1], lwd = 2, lty = 1, bty = "n")

  # Increment plot counter
  plot_count <- plot_count + 1
  
  # Start a new page after every four plots
  if (plot_count %% 4 == 0) {
    par(mfrow = c(2, 2))  # Reset the 2x2 grid for the next page
  }
}

# Close the PDF device
dev.off()

```

#rainfall Country level

```{r}
# Step 1: plot rainfall output
# Select the climate model 
model <- model0

# Extract full coef and vcov and create indicators for each term
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Find position of the terms associated with tmax crossbasis
indt <- grep("basis_tprainfall", model$names.fixed)

# Extract predictions from the rainfall DLNM
predt <- crosspred(basis_tprainfall, coef = coef[indt], vcov = vcov[indt, indt],
                   model.link = "log", bylag = 0.25, cen = round(mean(data$tprainfall, na.rm = TRUE), 0))

# Contour and scenario plots for rainfall (Main text Fig 3)
# Contour plot of exposure-lag-response associations (Main text Fig 3a)
pdf("figs4/fig_03a_rainfall_contour.pdf", width = 6.5, height = 6)

# Variables for plotting
y <- predt$predvar
x <- seq(0, nlag, 0.25)
z <- t(predt$matRRfit)

# Define color palettes and levels
pal <- rev(brewer.pal(11, "PRGn"))
levels <- pretty(range(z, na.rm = TRUE), 20)
col1 <- colorRampPalette(pal[1:6])
col2 <- colorRampPalette(pal[6:11])
cols <- c(col1(sum(levels <= 1)), col2(sum(levels > 1)))

# Generate filled contour plot
filled.contour(
  x, y, z,
  xlab = "Lag",
  ylab = expression(paste("Rainfall (", millimeter, "mm)")),
  main = "Diarrhea Under Five relative risk by rainfall",
  col = cols,
  levels = levels,
  plot.axes = {
    axis(1, at = 0:nlag, labels = 0:nlag)  # Customize x-axis
    axis(2)  # Customize y-axis
    mtext(side = 2, at = max(y) * 0.95, text = "a", las = 2, cex = 1.2, line = 2)
  }
)

# Close PDF device
if (dev.cur() > 1) dev.off()

```
# Plot Relative Risk by rainfall Range Only country level

```{r}
# Plot Relative Risk by rainfall Range Only

# Output plot as a high-resolution PNG
png("figs4/fig_relative_risk_rainfal.png", width = 800, height = 800, res = 150)

# Get exposure values
vars <- predt$predvar

# Ensure exposure values and RR data are finite
rr <- predt$matRRfit
rr.lci <- predt$matRRlow
rr.uci <- predt$matRRhigh

# Ensure there are no NA values in the data
if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
  stop("Missing values found in input data. Check 'predt' object.")
}

# Set colors for different temperature ranges
col <- colorRampPalette(brewer.pal(11, "RdBu"))(length(vars))

# Set y-axis limits dynamically based on RR range
r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

# Plot Relative Risk by Rainfall Range
plot(vars, rr[, 1], type = "l", col = col[1], lwd = 2,
     xlab = "Rainfall (mm)", ylab = "Relative Risk",
     main = "Diarrhea Under Five Relative Risk by rainfall Range",
     ylim = c(r1, r2 * 1.1), frame.plot = TRUE, axes = TRUE)

polygon(c(vars, rev(vars)),
        c(rr.lci[, 1], rev(rr.uci[, 1])),
        col = adjustcolor(col[1], alpha.f = 0.3), border = NA)

# Add horizontal reference line at RR = 1
abline(h = 1, lty = 2, col = "gray")

# Add a legend for rainfall ranges
legend("topright",
       legend = c("Relative Risk by rainfall Range"),
       col = col[1], lwd = 2, lty = 1, bty = "n")

# Save and close the PNG device
dev.off()
```


#Province level Rainfall

```{r}
# Load model output
load("output4/model0.3.RData")
model0 <- model

# Open a single PDF file for all provinces
pdf("figs4/fig_03a_rainfall_contour.pdf", width = 6.5, height = 6)

# Set up a consistent layout for the plots (1 per page)
par(mfrow = c(2,1 ))  # One plot per page

# Iterate over unique provinces
provinces <- unique(data$Province)
for (province in provinces) {
  # Filter data for the current province
  province_data <- subset(data, Province == province)

  # Set the model for the province
  model <- model0

# Extract full coef and vcov and create indicators for each term
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Extract predictions for the current province (assuming predt setup)
  mean_rainfall <- round(mean(province_data$tprainfall, na.rm = TRUE), 0)
  predt <- crosspred(basis_tprainfall, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_rainfall)

# Variables for plotting
y <- predt$predvar
x <- seq(0, nlag, 0.25)
z <- t(predt$matRRfit)

# Define color palettes and levels
pal <- rev(brewer.pal(11, "PRGn"))
levels <- pretty(range(z, na.rm = TRUE), 20)
col1 <- colorRampPalette(pal[1:6])
col2 <- colorRampPalette(pal[6:11])
cols <- c(col1(sum(levels <= 1)), col2(sum(levels > 1)))

# Generate filled contour plot
filled.contour(
  x, y, z,
  xlab = "Lag Month",
  ylab = expression(paste("Rainfall (", millimeter, "mm)")),
  main = paste("Contour Plot for", province),
  col = cols,
  levels = levels,
  plot.axes = {
    axis(1, at = 0:nlag, labels = 0:nlag)  # Customize x-axis
    axis(2)  # Customize y-axis
  }
)
}
# Close PDF device
if (dev.cur() > 1) dev.off()

```
# Plot Relative Risk by Precipitation Range Only for Each Province in a Single PDF

```{r}
# Set up a PDF output device for all plots
pdf("figs4/fig_relative_risk_rainfall_all_provinces.pdf", width = 10, height = 10)

provinces <- unique(data$Province)
layout(matrix(1:length(provinces), nrow = ceiling(sqrt(length(provinces))))) # Arrange plots in a grid
par(mfrow = c(3, 2)) 
for (province in provinces) {
  # Filter data for the current province
  province_data <- subset(data, Province == province)
  
  # Extract predictions for the current province (assuming predt setup)
  mean_rainfall <- round(mean(province_data$tprainfall, na.rm = TRUE), 0)
  predt <- crosspred(basis_tprainfall, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_rainfall)
  # Get exposure values
vars <- predt$predvar

# Ensure exposure values and RR data are finite
rr <- predt$matRRfit
rr.lci <- predt$matRRlow
rr.uci <- predt$matRRhigh

# Ensure there are no NA values in the data
if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
  stop("Missing values found in input data. Check 'predt' object.")
}

# Set colors for different temperature ranges
col <- colorRampPalette(brewer.pal(11, "RdBu"))(length(vars))

# Set y-axis limits dynamically based on RR range
r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

# Plot Relative Risk by Rainfall Range
plot(vars, rr[, 1], type = "l", col = col[1], lwd = 2,
     xlab = "Rainfall (mm)", ylab = "Relative Risk",
    main = paste("Diarrhea Under Five Relative Risk by rainfall for", province),
     ylim = c(r1, r2 * 1.1), frame.plot = TRUE, axes = TRUE)

polygon(c(vars, rev(vars)),
        c(rr.lci[, 1], rev(rr.uci[, 1])),
        col = adjustcolor(col[1], alpha.f = 0.3), border = NA)

# Add horizontal reference line at RR = 1
abline(h = 1, lty = 2, col = "gray")

# Add a legend for rainfall ranges
legend("topright",
       legend = c("Relative Risk by rainfall Range"),
       col = col[1], lwd = 2, lty = 1, bty = "n")

}
# Save and close the PNG device
dev.off()
  
```

#District level Rainfall


```{r}
# Load model output
load("output4/model0.3.RData")
model0 <- model

# Open a single PDF file for all districts
pdf("figs4/fig_03a_rainfall_contour_district.pdf", width = 6.5, height = 6)

# Set up a consistent layout for the plots (1 per page)
par(mfrow = c(2,2 ))  # One plot per page

# Iterate over unique districts
districts <- unique(data$District)
for (district in districts) {
  # Filter data for the current districts
  district_data <- subset(data, District == district)

  # Set the model for the district
  model <- model0

# Extract full coef and vcov and create indicators for each term
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Find position of terms associated with rainfall crossbasis
  indt <- grep("basis_tprainfall", model$names.fixed)

  # Extract predictions from the rainfall DLNM centered on overall mean Tmax
  mean_rainfall <- round(mean(district_data$tprainfall, na.rm = TRUE), 0)
  predt <- crosspred(basis_tprainfall, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_rainfall)

# Variables for plotting
y <- predt$predvar
x <- seq(0, nlag, 0.25)
z <- t(predt$matRRfit)

# Define color palettes and levels
pal <- rev(brewer.pal(11, "PRGn"))
levels <- pretty(range(z, na.rm = TRUE), 20)
col1 <- colorRampPalette(pal[1:6])
col2 <- colorRampPalette(pal[6:11])
cols <- c(col1(sum(levels <= 1)), col2(sum(levels > 1)))

# Generate filled contour plot
filled.contour(
  x, y, z,
  xlab = "Lag Month",
  ylab = expression(paste("Rainfall (", millimeter, "mm)")),
  main = paste("Contour Plot for", district),
  col = cols,
  levels = levels,
  plot.axes = {
    axis(1, at = 0:nlag, labels = 0:nlag)  # Customize x-axis
    axis(2)  # Customize y-axis
  }
)

  # Increment plot counter
  plot_count <- plot_count + 1

  # Start a new page after every four plots
  if (plot_count %% 4 == 0) {
    par(mfrow = c(2, 2))  # Reset 2x2 grid for the next page
  }
}
# Close PDF device
if (dev.cur() > 1) dev.off()

```

#District level relative risk plot

```{r}
# Set up a PDF output device for all plots
pdf("figs4/fig_relative_risk_rainfall_all_districts.pdf", width = 10, height = 10)

# Get unique districts
districts <- unique(data$District)

# Initialize counters
plot_count <- 0
total_plots <- length(districts)

# Loop over each district
for (i in seq_along(districts)) {
  district <- districts[i]
  
  # Filter data for the current district
  district_data <- subset(data, District == district)
  
  # Extract predictions for the current district
  mean_rainfall <- round(mean(district_data$tprainfall, na.rm = TRUE), 0)
  predt <- crosspred(basis_tprainfall, coef = coef[indt], vcov = vcov[indt, indt],
                     model.link = "log", bylag = 0.25, cen = mean_rainfall)

  # Get exposure values
  vars <- predt$predvar

  # Ensure exposure values and RR data are finite
  rr <- predt$matRRfit
  rr.lci <- predt$matRRlow
  rr.uci <- predt$matRRhigh

  # Ensure there are no NA values in the data
  if (anyNA(c(vars, rr, rr.lci, rr.uci))) {
    stop("Missing values found in input data. Check 'predt' object.")
  }

  # Set colors for different rainfall ranges
  col <- colorRampPalette(brewer.pal(11, "RdBu"))(length(vars))

  # Set y-axis limits dynamically based on RR range
  r1 <- min(c(rr, rr.lci, rr.uci), na.rm = TRUE)
  r2 <- max(c(rr, rr.lci, rr.uci), na.rm = TRUE)

  # Set up new page for every 4 plots
  if (plot_count %% 4 == 0) {
    par(mfrow = c(2, 2))  # Set 2x2 layout for 4 plots per page
  }

  # Plot Relative Risk by Rainfall Range
  plot(vars, rr[, 1], type = "l", col = col[1], lwd = 2,
       xlab = "Rainfall (mm)", ylab = "Relative Risk",
       main = paste("Diarrhea Under Five Relative Risk by Rainfall for", district),
       ylim = c(r1, r2 * 1.1), frame.plot = TRUE, axes = TRUE)

  polygon(c(vars, rev(vars)),
          c(rr.lci[, 1], rev(rr.uci[, 1])),
          col = adjustcolor(col[1], alpha.f = 0.3), border = NA)

  # Add horizontal reference line at RR = 1
  abline(h = 1, lty = 2, col = "gray")

  # Add a legend for rainfall ranges
  legend("topright",
         legend = c("Relative Risk by Rainfall Range"),
         col = col[1], lwd = 2, lty = 1, bty = "n")

  # Increment plot counter
  plot_count <- plot_count + 1

  # Reset layout after the last plot on the current page
  if (plot_count %% 4 == 0 || i == total_plots) {
    par(mfrow = c(1, 1))  # Reset layout after every page or at the end
  }
}

# Save and close the PDF device
dev.off()

```

#rainfall scenarios
```{r}
# Lag response for different rainfall scenarios (Main text Fig 3b)
pdf("figs4/fig_03b_rainfall_scenario.pdf", width = 6, height = 6)

# Get exposure values
vars <- predt$predvar

# Debug: Print exposure values to confirm target matches
print(vars)

# Obtain relative risk (RR) fit and upper/lower confidence limits
rr <- predt$matRRfit
rr.lci <- predt$matRRlow
rr.uci <- predt$matRRhigh

# Debug: Print dimensions
print(dim(rr))
print(dim(rr.lci))
print(dim(rr.uci))

# Adjust lagbylag to match rr dimensions
lagbylag <- seq(0, ncol(rr) - 1) * 0.25

# Debug: Print lagbylag
print(length(lagbylag))

# Get selected exposure variable positions with approximate matching
mn <- which.min(abs(vars - 200))
mx <- which.min(abs(vars - 600))
mx2 <- which.min(abs(vars - 800))

# Debug: Print indices
print(mn); print(mx); print(mx2)

# Define colors
col1 <- brewer.pal(11, "RdBu")[9]
tcol1 <- do.call(rgb, c(as.list(col2rgb(col1)), alpha = 255/4, max = 255))

col2 <- brewer.pal(11, "RdBu")[3]
tcol2 <- do.call(rgb, c(as.list(col2rgb(col2)), alpha = 255/4, max = 255))

col3 <- brewer.pal(11, "RdBu")[1]
tcol3 <- do.call(rgb, c(as.list(col2rgb(col3)), alpha = 255/4, max = 255))

# Set relative risk range
r1 <- min(range(rr, rr.lci, rr.uci, na.rm = TRUE))
r2 <- max(range(rr, rr.lci, rr.uci, na.rm = TRUE))
r <- range(rr, rr.lci, rr.uci, na.rm = TRUE)
# Cool scenario
plot(lagbylag, rr[mn,], col = col1, type = "l", lwd = 1, 
     xlab = "Lag", ylab = "Relative risk", main = "", 
     ylim = c(r1, r2 * 1.1), frame.plot = TRUE, axes = FALSE)
axis(1, at = seq(0, max(lagbylag), 1), labels = seq(0, max(lagbylag), 1))
axis(2)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[mn,], rev(rr.uci[mn,]))
polygon(xx, yy, col = tcol1, border = tcol1)

# Warm scenario
lines(lagbylag, rr[mx,], col = col2, lwd = 1)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[mx,], rev(rr.uci[mx,]))
polygon(xx, yy, col = tcol2, border = tcol2)

# Warmest scenario
lines(lagbylag, rr[mx2,], col = col3, lwd = 1)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[mx2,], rev(rr.uci[mx2,]))
polygon(xx, yy, col = tcol3, border = tcol3)

abline(h = 1, lty = 3)

# Legend
legend("topleft",
       legend = c(paste0("rainfall = ", round(vars[mn], 1), " mm "),
                  paste0("rainfall = ", round(vars[mx], 1), " mm "),
                  paste0("rainfall = ", round(vars[mx2], 1), " mm ")),
       col = c(col1, col2, col3), 
       lwd = 2, lty = 1, bty = "n", 
       y.intersp = 1.5, horiz = FALSE)

# Add subplot label
mtext(side = 2, at = r2 * 1.1, text = "b", las = 2, cex = 1.2, line = 2)

# Close PDF device
dev.off()
```



#Attributable number and fraction calculation


```{r}
# (READ THE ACCOMPANYING PDF FOR DOCUMENTATION)
source("attrdl.R")
#data$Diarrhea_Hosp_OPD_ud_five
```

```{r}
# Load best-fitting model with climate DLNMs
load("output4/model0.3.RData")
model <- model0  # Ensure model0 is loaded correctly

# Extract full coefficients and covariance matrix
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Find the position of terms associated with the temperature crossbasis
indt <- grep("basis_tmax", model$names.fixed)

# Validate model data and inputs
if (is.null(coef) || is.null(vcov)) stop("Model coefficients or covariance matrix are missing.")
if (length(indt) == 0) stop("No terms associated with 'basis_tmax' found in the model.")

# Recreate the temperature crossbasis (cb) using the original structure
nlag <- 2  # Infer the number of lags
if (nlag == 0) stop("Lagged variables not found in the data.")

cb <- crossbasis(
  subset(data, select = c("temp", paste0("tp_lag", 1:nlag))),
  argvar = list(fun = "ns", knots = equalknots(data$temp, 2)),  # Use equalknots with reproducibility
  arglag = list(fun = "ns", knots = nlag / 2)
)

# Calculate center temperature for predictions
cen <- round(mean(data$temp, na.rm = TRUE), 0)

# Validate temperature data
if (is.na(cen)) stop("Center temperature (cen) calculation failed due to missing data.")

# Define minimum and maximum temperatures from the data
min_temp <- min(data$temp, na.rm = TRUE)
max_temp <- max(data$temp, na.rm = TRUE)

# Predict relative risks over a range of temperatures using crosspred
temp_range <- seq(min_temp, max_temp, by = 0.1)  # Define temperature range

# Generate predictions using the crossbasis, coefficients, and covariance matrix
predt <- crosspred(cb, coef = coef[indt], vcov = vcov[indt, indt], model.link = "log", at = temp_range, cen = cen)

# Find the Minimum Risk Temperature (MRT)
mrt <- predt$predvar[which.min(predt$allRRfit)]
mrt_ci <- quantile(predt$allRRfit, probs = c(0.025, 0.975))  # Confidence interval for MRT

# Output MRT range
print(paste("Minimum Risk Temperature (MRT):", mrt))
print(paste("Confidence Interval for MRT:", round(mrt_ci[1], 2), "to", round(mrt_ci[2], 2)))

# Define the temperature range where RR > 1 (i.e., the RR exceeds 1)
high_temp_range <- temp_range[predt$allRRfit > 1.1]

# If the high_temp_range is empty, there are no temperatures where RR > 1
if (length(high_temp_range) == 0) {
  cat("No temperatures found where RR > 1.\n")
  next
}

# Find the temperature bounds where RR > 1.1
high_temp_bounds <- range(high_temp_range)  # Lower and upper bounds

# Attributable risk calculations for temperatures where RR > 1.1
an_risk_number_hot <- attrdl(
  data$temp, cb, data$Diarrhea_Hosp_OPD_ud_five, 
  coef = coef[indt], vcov = vcov[indt, indt], 
  type = "an", cen = mrt, range = high_temp_bounds
)

an_risk_fraction_hot <- attrdl(
  data$temp, cb, data$Diarrhea_Hosp_OPD_ud_five, 
  coef = coef[indt], vcov = vcov[indt, indt], 
  type = "af", cen = mrt, range = high_temp_bounds
)

# Output the results for extreme high temperatures
cat("Attributable Risk for High Temperatures (RR > 1.1):\n")
cat("  High Temperature Range:", round(high_temp_bounds[1], 2), "to", round(high_temp_bounds[2], 2), "\n")
cat("  Attributable Risk (Number):", round(an_risk_number_hot), "\n")
cat("  Attributable Risk (Fraction):", round(an_risk_fraction_hot * 100, 2), "%\n")
```


## Attributable Risk of Extreme Hot Temperatures for each province and year
```{r}

# Load best-fitting model with climate DLNMs
load("output4/model0.3.RData")
model <- model0  # Ensure model0 is loaded correctly

# Extract full coefficients and covariance matrix
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Find the position of terms associated with the temperature crossbasis
indt <- grep("basis_tmax", model$names.fixed)

# Validate model data and inputs
if (is.null(coef) || is.null(vcov)) stop("Model coefficients or covariance matrix are missing.")
if (length(indt) == 0) stop("No terms associated with 'basis_tmax' found in the model.")

# Recreate the temperature crossbasis (cb) using the original structure
nlag <- 2  # Infer the number of lags
if (nlag == 0) stop("Lagged variables not found in the data.")

# Initialize results storage
results <- data.frame(
  Province = character(),
  Year = integer(),
  MRT = numeric(),
  High_Temperature_Lower = numeric(),
  High_Temperature_Upper = numeric(),
  Attributable_Risk_Number = numeric(),
  Attributable_Risk_Fraction = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each province and year
for (prov in unique(data$Province)) {
  
  for (year in unique(data$Year)) {
    
    # Subset data for the current province and year
    data_prov_year <- subset(data, Province == prov & Year == year)

    # Skip if insufficient data for the province and year
    if (nrow(data_prov_year) < 10) next

    # Recreate the temperature crossbasis for the province and year
    cb_prov_year <- crossbasis(
      subset(data_prov_year, select = c("temp", paste0("tp_lag", 1:nlag))),
      argvar = list(fun = "ns", knots = equalknots(data_prov_year$temp, 2)),
      arglag = list(fun = "ns", knots = nlag / 2)
    )

    # Calculate center temperature for predictions
    cen <- round(mean(data_prov_year$temp, na.rm = TRUE), 0)

    # Validate temperature data
    if (is.na(cen)) next

    # Define minimum and maximum temperatures from the data
    min_temp <- min(data_prov_year$temp, na.rm = TRUE)
    max_temp <- max(data_prov_year$temp, na.rm = TRUE)
    temp_range <- seq(min_temp, max_temp, by = 0.1)

    # Generate predictions using the crossbasis, coefficients, and covariance matrix
    predt <- crosspred(cb_prov_year, coef = coef[indt], vcov = vcov[indt, indt], model.link = "log", at = temp_range, cen = cen)

    # Find the Minimum Risk Temperature (MRT)
    mrt <- predt$predvar[which.min(predt$allRRfit)]

    # Define the temperature range where RR > 1.1 (i.e., the RR exceeds 1.1)
    high_temp_range <- temp_range[predt$allRRfit > 1.1]

    # If the high_temp_range is empty, there are no temperatures where RR > 1.1
    if (length(high_temp_range) == 0) {
      next
    }

    # Find the temperature bounds where RR > 1
    high_temp_bounds <- range(high_temp_range)  # Lower and upper bounds

    # Attributable risk calculations for temperatures where RR > 1.1
    an_risk_number_hot <- attrdl(
      data_prov_year$temp, cb_prov_year, data_prov_year$Diarrhea_Hosp_OPD_ud_five, 
      coef = coef[indt], vcov = vcov[indt, indt], 
      type = "an", cen = mrt, range = high_temp_bounds
    )

    an_risk_fraction_hot <- attrdl(
      data_prov_year$temp, cb_prov_year, data_prov_year$Diarrhea_Hosp_OPD_ud_five, 
      coef = coef[indt], vcov = vcov[indt, indt], 
      type = "af", cen = mrt, range = high_temp_bounds
    )

    # Store results for the current province and year
    results <- rbind(results, data.frame(
      Province = prov,
      Year = year,
      MRT = round(mrt, 2),
      High_Temperature_Lower = round(high_temp_bounds[1], 2),
      High_Temperature_Upper = round(high_temp_bounds[2], 2),
      Attributable_Risk_Number = round(an_risk_number_hot),
      Attributable_Risk_Fraction = round(an_risk_fraction_hot * 100, 2)
    ))
  }
}

# Display results for all provinces and years
print(results)
# Save results to CSV
write.csv(results, "output4/attribution_temp_per_province_year.csv", row.names = FALSE)

```

#Attributable Risk of Extreme Hot Temperatures for each district and year

```{r}
# Load best-fitting model with climate DLNMs
load("output4/model0.3.RData")
model <- model0  # Ensure model0 is loaded correctly

# Extract full coefficients and covariance matrix
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Find the position of terms associated with the temperature crossbasis
indt <- grep("basis_tmax", model$names.fixed)

# Validate model data and inputs
if (is.null(coef) || is.null(vcov)) stop("Model coefficients or covariance matrix are missing.")
if (length(indt) == 0) stop("No terms associated with 'basis_tmax' found in the model.")

# Recreate the temperature crossbasis (cb) using the original structure
nlag <- 2  # Infer the number of lags
if (nlag == 0) stop("Lagged variables not found in the data.")

# Initialize results storage
results <- data.frame(
  Province = character(),
  District = character(),
  Year = integer(),
  MPR = numeric(),
  High_Temperature_Lower = numeric(),
  High_Temperature_Upper = numeric(),
  Attributable_Risk_Number = numeric(),
  Attributable_Risk_Fraction = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each province, district, and year
for (prov in unique(data$Province)) {
  for (district in unique(data$District)) {
    for (year in unique(data$Year)) {
      
      # Subset data for the current province, district, and year
      data_group <- subset(data, Province == prov & District == district & Year == year)

      # Skip if insufficient data
      if (nrow(data_group) < 10) next

      # Recreate the temperature crossbasis for the group
      cb_group <- crossbasis(
        subset(data_group, select = c("temp", paste0("tp_lag", 1:nlag))),
        argvar = list(fun = "ns", knots = equalknots(data_group$temp, 2)),
        arglag = list(fun = "ns", knots = nlag / 2)
      )

      # Calculate center temperature for predictions
      cen <- round(mean(data_group$temp, na.rm = TRUE), 0)

      # Validate temperature data
      if (is.na(cen)) next

      # Define minimum and maximum temperatures from the data
      min_temp <- min(data_group$temp, na.rm = TRUE)
      max_temp <- max(data_group$temp, na.rm = TRUE)
      temp_range <- seq(min_temp, max_temp, by = 0.1)

      # Generate predictions using the crossbasis, coefficients, and covariance matrix
      predt <- crosspred(cb_group, coef = coef[indt], vcov = vcov[indt, indt], model.link = "log", at = temp_range, cen = cen)

      # Find the Minimum Risk Temperature (MRT)
      mrt <- predt$predvar[which.min(predt$allRRfit)]

      # Define the temperature range where RR > 1.1 (i.e., the RR exceeds 1.1)
      high_temp_range <- temp_range[predt$allRRfit > 1.1]

      # If the high_temp_range is empty, there are no temperatures where RR > 1
      if (length(high_temp_range) == 0) {
        next
      }

      # Find the temperature bounds where RR > 1
      high_temp_bounds <- range(high_temp_range)  # Lower and upper bounds

      # Attributable risk calculations for temperatures where RR > 1.1
      an_risk_number_hot <- attrdl(
        data_group$temp, cb_group, data_group$Diarrhea_Hosp_OPD_ud_five, 
        coef = coef[indt], vcov = vcov[indt, indt], 
        type = "an", cen = mrt, range = high_temp_bounds
      )

      an_risk_fraction_hot <- attrdl(
        data_group$temp, cb_group, data_group$Diarrhea_Hosp_OPD_ud_five, 
        coef = coef[indt], vcov = vcov[indt, indt], 
        type = "af", cen = mrt, range = high_temp_bounds
      )

      # Store results for the current group
      results <- rbind(results, data.frame(
        Province = prov,
        District = district,
        Year = year,
        MPR = round(mrt, 2),
        High_Temperature_Lower = round(high_temp_bounds[1], 2),
        High_Temperature_Upper = round(high_temp_bounds[2], 2),
        Attributable_Risk_Number = round(an_risk_number_hot),
        Attributable_Risk_Fraction = round(an_risk_fraction_hot * 100, 2)
      ))
    }
  }
}

# Display results for all groups
print(results)
# Save results to CSV
write.csv(results, "output4/attribution_temp_per_district_year.csv", row.names = FALSE)

```

##Country level attribution risk rainfall
```{r}
# Load best-fitting model with climate DLNMs
load("output4/model0.3.RData")

# Select the model
model <- model0

# Extract coefficients and covariance matrix
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Identify terms related to the rainfall crossbasis
indr <- grep("basis_tprainfall", model$names.fixed)

# Validate model inputs
if (is.null(coef) || is.null(vcov)) stop("Model coefficients or covariance matrix are missing.")
if (length(indr) == 0) stop("No terms associated with 'basis_tprainfall' found in the model.")

# Recreate the rainfall crossbasis for the entire dataset
nlag <- 2  # Number of lags
cb <- crossbasis(
  subset(data, select = c("tprainfall", paste0("rtp_lag", 1:nlag))),
  argvar = list(fun = "ns", knots = equalknots(data$tprainfall, 2)),
  arglag = list(fun = "ns", knots = lagknot)
)

# Center rainfall value for predictions
cen <- round(mean(data$tprainfall, na.rm = TRUE), 0)

# Validate precipitation data
if (is.na(cen)) stop("Center rainfall (cen) calculation failed due to missing data.")

# Define minimum and maximum precipitation from the data
min_rainfall <- min(data$tprainfall, na.rm = TRUE)
max_rainfall <- max(data$tprainfall, na.rm = TRUE)

# Predict relative risks over a range of rainfall using crosspred
rain_range <- seq(min_rainfall, max_rainfall, by = 0.1)  # Define precipitation range

# Generate predictions using the crossbasis, coefficients, and covariance matrix
predt <- crosspred(cb, coef = coef[indr], vcov = vcov[indr, indr], model.link = "log", at = rain_range, cen = cen)

# Find the Minimum Precipitation Risk (MPR)
mpr <- predt$predvar[which.min(predt$allRRfit)]
mpr_ci <- quantile(predt$allRRfit, probs = c(0.025, 0.975))  # Confidence interval for MPR

# Define the precipitation range where RR > 1.1
high_rainfall_range <- rain_range[predt$allRRfit > 1.05]
high_rainfall_bounds <- range(high_rainfall_range)  # Lower and upper bounds

# Attributable risk calculations for the high precipitation range
an_risk_number_rain <- attrdl(
  data$tprainfall, cb, data$Diarrhea_Hosp_OPD_ud_five, 
  coef = coef[indr], vcov = vcov[indr, indr], 
  type = "an", cen = mpr, range = high_rainfall_bounds
)

an_risk_fraction_rain <- attrdl(
  data$tprainfall, cb, data$Diarrhea_Hosp_OPD_ud_five, 
  coef = coef[indr], vcov = vcov[indr, indr], 
  type = "af", cen = mpr, range = high_rainfall_bounds
)

# Output the results
cat("\nPrecipitation Risk Summary:\n")
cat("  Minimum Precipitation Risk (MPR):", mpr, "\n")
cat("  95% CI for MPR:", mpr_ci[1], "-", mpr_ci[2], "\n")
cat("  High Precipitation Range (RR > 1):", high_rainfall_bounds[1], "to", high_rainfall_bounds[2], "\n")
cat("  Attributable Risk (Number):", round(an_risk_number_rain), "\n")
cat("  Attributable Risk (Fraction):", round(an_risk_fraction_rain * 100, 2), "%\n")

```


## attribution risk rainfall provice for each year

```{r}
# Load best-fitting model with climate DLNMs
load("output4/model0.3.RData")

# Select the model
model <- model0

# Extract coefficients and covariance matrix
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Identify terms related to the rainfall crossbasis
indr <- grep("basis_tprainfall", model$names.fixed)

# Validate model inputs
if (is.null(coef) || is.null(vcov)) stop("Model coefficients or covariance matrix are missing.")
if (length(indr) == 0) stop("No terms associated with 'basis_tprainfall' found in the model.")

# List unique provinces and years
provinces <- unique(data$Province)
years <- unique(data$Year)  # Assuming "Year" is a column in the dataset

# Initialize results storage
results <- data.frame(
  Province = character(),
  Year = integer(),
  MPR = numeric(),
  High_Precipitation_Lower = numeric(),
  High_Precipitation_Upper = numeric(),
  Attributable_Risk_Number = numeric(),
  Attributable_Risk_Fraction = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each province
for (prov in provinces) {
  
  # Subset data for the province
  data_prov <- subset(data, Province == prov)

  # Skip if insufficient data
  if (nrow(data_prov) < 10) next

  # Loop through each year within the province
  for (yr in years) {
    
    # Subset data for the specific year
    data_year <- subset(data_prov, Year == yr)
    
    if (nrow(data_year) < 10) next  # Skip years with insufficient data

    # Recreate the rainfall crossbasis
    nlag <- 2  # Number of lags
    cb_year <- crossbasis(
      subset(data_year, select = c("tprainfall", paste0("rtp_lag", 1:nlag))),
      argvar = list(fun = "ns", knots = equalknots(data_year$tprainfall, 2)),
      arglag = list(fun = "ns", knots = lagknot)
    )

    # Center rainfall value for predictions
    cen <- round(mean(data_year$tprainfall, na.rm = TRUE), 0)

    # Validate precipitation data
    if (is.na(cen)) next

    # Define precipitation range
    min_rainfall <- min(data_year$tprainfall, na.rm = TRUE)
    max_rainfall <- max(data_year$tprainfall, na.rm = TRUE)
    rain_range <- seq(min_rainfall, max_rainfall, by = 0.1)

    # Generate predictions using the crossbasis, coefficients, and covariance matrix
    predt <- crosspred(cb_year, coef = coef[indr], vcov = vcov[indr, indr], model.link = "log", at = rain_range, cen = cen)

    # Find the Minimum Precipitation Risk (MPR)
    mpr <- predt$predvar[which.min(predt$allRRfit)]

    # Define the precipitation range where RR > 1.1
    high_rainfall_range <- rain_range[predt$allRRfit > 1.1]
    
    if (length(high_rainfall_range) == 0) next  # Skip if no high-risk range found

    high_rainfall_bounds <- range(high_rainfall_range)  # Lower and upper bounds

    # Attributable risk calculations for high precipitation range
    an_risk_number_rain <- attrdl(
      data_year$tprainfall, cb_year, data_year$Diarrhea_Hosp_OPD_ud_five, 
      coef = coef[indr], vcov = vcov[indr, indr], 
      type = "an", cen = mpr, range = high_rainfall_bounds
    )

    an_risk_fraction_rain <- attrdl(
      data_year$tprainfall, cb_year, data_year$Diarrhea_Hosp_OPD_ud_five, 
      coef = coef[indr], vcov = vcov[indr, indr], 
      type = "af", cen = mpr, range = high_rainfall_bounds
    )

    # Store results in a data frame
    results <- rbind(results, data.frame(
      Province = prov,
      Year = yr,
      MPR = round(mpr, 2),
      High_Precipitation_Lower = round(high_rainfall_bounds[1], 2),
      High_Precipitation_Upper = round(high_rainfall_bounds[2], 2),
      Attributable_Risk_Number = round(an_risk_number_rain),
      Attributable_Risk_Fraction = round(an_risk_fraction_rain * 100, 2)
    ))
  }
}

# Display results
print(results)

# Save results to CSV
write.csv(results, "output4/attribution_rainfall_province_per_year.csv", row.names = FALSE)

```

##attribution risk rainfall by district for each year

```{r}
# Load best-fitting model with climate DLNMs
load("output4/model0.3.RData")

# Select the model
model <- model0

# Extract coefficients and covariance matrix
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix

# Identify terms related to the rainfall crossbasis
indr <- grep("basis_tprainfall", model$names.fixed)

# Validate model inputs
if (is.null(coef) || is.null(vcov)) stop("Model coefficients or covariance matrix are missing.")
if (length(indr) == 0) stop("No terms associated with 'basis_tprainfall' found in the model.")

# List unique provinces, districts, and years
provinces <- unique(data$Province)
districts <- unique(data$District)
years <- unique(data$Year)  # Assuming "Year" is a column in the dataset

# Initialize results storage
results <- data.frame(
  Province = character(),
  District = character(),
  Year = integer(),
  MPR = numeric(),
  High_Precipitation_Lower = numeric(),
  High_Precipitation_Upper = numeric(),
  Attributable_Risk_Number = numeric(),
  Attributable_Risk_Fraction = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each province
for (prov in provinces) {
  
  # Subset data for the province
  data_prov <- subset(data, Province == prov)

  # Skip if insufficient data
  if (nrow(data_prov) < 10) next

  # Loop through each district within the province
  for (dist in districts) {
    
    # Subset data for the specific district
    data_dist <- subset(data_prov, District == dist)
    
    if (nrow(data_dist) < 10) next  # Skip districts with insufficient data

    # Loop through each year within the district
    for (yr in years) {
      
      # Subset data for the specific year
      data_year <- subset(data_dist, Year == yr)
      
      if (nrow(data_year) < 10) next  # Skip years with insufficient data

      # Recreate the rainfall crossbasis
      nlag <- 2  # Number of lags
      cb_year <- crossbasis(
        subset(data_year, select = c("tprainfall", paste0("rtp_lag", 1:nlag))),
        argvar = list(fun = "ns", knots = equalknots(data_year$tprainfall, 2)),
        arglag = list(fun = "ns", knots = lagknot)
      )

      # Center rainfall value for predictions
      cen <- round(mean(data_year$tprainfall, na.rm = TRUE), 0)

      # Validate precipitation data
      if (is.na(cen)) next

      # Define precipitation range
      min_rainfall <- min(data_year$tprainfall, na.rm = TRUE)
      max_rainfall <- max(data_year$tprainfall, na.rm = TRUE)
      rain_range <- seq(min_rainfall, max_rainfall, by = 0.1)

      # Generate predictions using the crossbasis, coefficients, and covariance matrix
      predt <- crosspred(cb_year, coef = coef[indr], vcov = vcov[indr, indr], model.link = "log", at = rain_range, cen = cen)

      # Find the Minimum Precipitation Risk (MPR)
      mpr <- predt$predvar[which.min(predt$allRRfit)]

      # Define the precipitation range where RR > 1
      high_rainfall_range <- rain_range[predt$allRRfit > 1]
      
      if (length(high_rainfall_range) == 0) next  # Skip if no high-risk range found

      high_rainfall_bounds <- range(high_rainfall_range)  # Lower and upper bounds

      # Attributable risk calculations for high precipitation range
      an_risk_number_rain <- attrdl(
        data_year$tprainfall, cb_year, data_year$Diarrhea_Hosp_OPD_ud_five, 
        coef = coef[indr], vcov = vcov[indr, indr], 
        type = "an", cen = mpr, range = high_rainfall_bounds
      )

      an_risk_fraction_rain <- attrdl(
        data_year$tprainfall, cb_year, data_year$Diarrhea_Hosp_OPD_ud_five, 
        coef = coef[indr], vcov = vcov[indr, indr], 
        type = "af", cen = mpr, range = high_rainfall_bounds
      )

      # Store results in a data frame
      results <- rbind(results, data.frame(
        Province = prov,
        District = dist,
        Year = yr,
        MPR = round(mpr, 2),
        High_Precipitation_Lower = round(high_rainfall_bounds[1], 2),
        High_Precipitation_Upper = round(high_rainfall_bounds[2], 2),
        Attributable_Risk_Number = round(an_risk_number_rain),
        Attributable_Risk_Fraction = round(an_risk_fraction_rain * 100, 2)
      ))
    }
  }
}

# Display results
print(results)

# Save results to CSV
write.csv(results, "output4/attribution_per_district_year.csv", row.names = FALSE)

```

